Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-31 article/draft.tex
add detail about yt policy

YouTube provide information panel at the top of search results or under a video related to topics prone to misinformation.
Information panels provide more context on a controversial matter, with a link to an independent, third-party partner's website such as Wikipedia or the World Health Organization. 
Importantly, YouTube states that these panels exist regardless of the point of view expressed in a given video.\footnote{https://support.google.com/youtube/answer/9004474}

@@

{\bf Channel Level.} 
The $3$ $895$ unique videos came from $1$ $562$ different channels, and we counted the number of times every channel got recommended.
Figure \ref{reduce_youtube} shows the top $10$ recommended channels, whose videos represent $30\%$ of the recommendations.
Fox News and Sky News Australia, which both have a ``mixed'' factual reporting level according to {\it iffy.news} and have several failed fact-checks,\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/} and \href{https://mediabiasfactcheck.com/sky-news-australia/}{https://mediabiasfactcheck.com/sky-news-australia/}.} are at the first and third place respectively.
PragerU is also among the list of the 10 most recommended channel, with a ``low'' level of factual reporting according to {\it iffy.news}.

>>>>

YouTube provide information panel at the top of search results or under a video related to topics prone to misinformation.
Information panels provide more context on a controversial matter, with a link to an independent, third-party partner's website such as Wikipedia or the World Health Organization. 
Importantly, YouTube states that these panels exist regardless of the point of view expressed in a given video.
YouTube also specifies that information panels may not be available in all countries/regions and languages.\footnote{https://support.google.com/youtube/answer/9004474}

@@

{\bf Channel Level.} 
The $3$ $895$ unique videos came from $1$ $562$ different channels, and we counted the number of times every channel got recommended.
Figure \ref{reduce_youtube} shows the top $10$ recommended channels, whose videos represent $30\%$ of the recommendations.
Fox News and Sky News Australia, which both have a ``mixed'' factual reporting level according to {\it iffy.news} and have several failed fact-checks,\footnote{See \href{https://mediabiasfactcheck.com/fox-news-bias/}{https://mediabiasfactcheck.com/fox-news-bias/} and \href{https://mediabiasfactcheck.com/sky-news-australia/}{https://mediabiasfactcheck.com/sky-news-australia/}.} are at the first and third place respectively.
PragerU is also among the list of the 10 most recommended channels, with a ``low'' level of factual reporting according to {\it iffy.news}.
